\section*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

First of all, many thanks go to my supervisors Duncan Brumby and Anna Cox for being such a great supervisory team. Duncan for challenging me on why I am doing things the way I do, and Anna for questioning how these things contribute to the big picture. Their guidance, feedback and support have helped me ensure my work was held to a high standard.

%But most of all, thanks for being accessible and available at all times. 

Thanks to Ann Blandford for examining my first-year and upgrade vivas. The feedback was critical in shaping this thesis.

%I also owe a big thank you to
I would also like to thank everyone at UCLIC - being surrounded by such an amazing group of people made the PhD a lot less lonely, and I will miss the daily lunches, chats, and laughs. Thanks to Sarah and Sandy for all their helpful advice when I got started, and for sharing my enthusiasm about data entry and interruptions - which admittedly is a niche thing to get excited about.
Thanks to Louise for always helping out with various things and making sure everything runs smoothly.
And thank you to all academics I had the opportunity to work with on the MSc course, for teaching me about teaching.

During the last part of my PhD, I was fortunate to work at Microsoft Research. Having breaks from my PhD, and being able to collaborate with various researchers approaching problems from different perspectives, helped me go back to my research with a fresh and refocused look. In particular thanks to my mentors Kenton O'Hara and Andy Gordon for always challenging and encouraging me to improve. 

I would also like to thank my MSc supervisor Paul Cairns: my master's project on number entry in 2013 was what inspired me to pursue a PhD in data entry at UCL. 

%Thanks also to David McKee, for proofreading parts of this thesis. 

The studies in this thesis depended on participants, and I am very grateful for their time and willingness to take part in the studies.

Thanks to my friends for their support, being a listening ear and being understanding regarding my erratic work schedule - I am sorry for all the events I have had to miss last-minute!

Throughout my life Taekwondo has been a fundamental part of my routine. These past years it has played an essential role in maintaining a healthy work-life balance, and in providing a much needed stress release. For this I owe thanks to everyone at my Taekwondo club, especially my coach Amar. Thank you all for the training sessions, competitions, for shouting at me, and for truly being one big family. 

Finally, I would like to thank my parents, my sister, and everyone else in my family for their unconditional love and support in all of my pursuits. Their trust and words of encouragement have helped me follow my instinct and pursue what I love to do, no matter where in the world it may take me.